### 2016-07-22 intro.tex
restructuring

\jnote{Are we being too specific by focusing on hash-based
set-membership only? It would be nice to give general definitions
that apply to arbitrary data structures (constructed in arbitrary
ways) and then only later specialized to hash-based Bloom filters.
(Put this in an appendix for now, until we see how things play
out.)}

\section{Introduction}
We revisit the formalization of Bloom filters~\cite{xxx} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admiting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.

Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.  Let us explain.

Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$. The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).  The query algorithm~$\mathcal{B}_2$ is deterministic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.  For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.  For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''. First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set $\mathcal{S}$ that can be adversarially chosen. Then the adversary may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.  At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.

First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.  On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.  On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.  Our notions will address both sides of this discussion.
%
%\jnote{We discussed this on the phone, but let me put it in writing here. I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
%
%\tsnote{For me the question is: is security violated once the first FP is found, or the second? My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards. But I do appreciate your point.  A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.  Adapting to what, though? In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.  The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.  The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.  The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.  Each has it's own associated (informal) security interpretation.}
%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle). Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.  Right?}
%
%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; \jnote{I think this is also reasonable; typically
security is defined without regard for efficiency} \tsnote{My
complaint isn't about efficiency. It's about the fact that, by not
including $|M|$ in the definition, the trivial scheme I give (just
below) is allowed, and is secure.  Anyway, as I say at the end of
this paragraph, this is a small(er) complaint than what follows}.
\jnote{I would say that the trivial scheme \emph{is} secure!}
\tsnote{Okay, well then we need some way to ``rule out'' the trivial
solution. Perhaps just in the text -- yes, the trivial scheme works,
but it isn't interesting in practice. Also, in the concrete security
bounds that we will prove, the size of the representation is going
to come up, e.g.\ the number of bits in the BF array directly affect
the FP rate. Hence it makes sense to say things like ``an
$(n,k,m)$-filter\ldots'' where $m$ is the size of the
representation.} \jnote{I still disagree: efficiency is orthogonal
to functionality and security.} The surrounding text does say that
$\mathbf{B}_1$ ``outputs a compressed representation [of
$\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this
means is never addressed. The formal syntax admits
$\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints. But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

In particular, say we implement a classic Bloom filter.  Then the hash functions $h_1, h_2, \ldots, h_k$ are either sampled from some family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.  Let's assume the former for the moment.  In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well. Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.  But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.  Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds. Moreover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations.
%Thus, if we assume that
%$\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their
%formalization fails to capture the basic Bloom filter construction;
%at best, it is hard to see clearly that it does.

%\jnote{FWIW, I think the classical description of Bloom filters has the same problem. I.e., if the hash functions are not fixed, then their description should be counted as part of the length of the data structure. On the other hand, if they are fixed, then the false-positive rate is not well-defined (since there is no probability space to speak of). So in that sense, NY just carried over the problem from the classical literature.}
%
%\tsnote{One can suggest that it \emph{should} be counted in the classical description, but the fact is that it isn't :) And in the 30+ years since the original paper, no one saw fit to correct this? From an algorithmic perspective, I think the classical approach makes sense.  The questions being answered are: how many bits do I need to store a representation of the set for a given FP rate, and how does this compare to the combinatorially computed lower-bound? The description length of the hash functions may be bigger or smaller, but the number of bits you need to hold the set representation is independent of that.  (Imagine that you have long random bitstrings in the set~$\mathcal{S}$.  Then whether your hash functions simply truncate, or they are random oracles, the size of the representation as a function of the target FP rate doesn't change.  Yet the description lengths of the hash functions are drastically different.)}

On the other hand, assume the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$). Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.  If the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$, then the adversary can compute~$M$ itself, as well as test for false positives itself. So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive. Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.  So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
\jnote{Perhaps it is reasonable to consider a definition in which the set is not given to the adversary?}
\tsnote{A FP security notion? Yes, perhaps so.  It's probably a more realistic notion anyway -- is a spammer really going to know my whitelist a priori? (If he does, I probably have bigger problems in my system than receiving new spam email.) Or set of URLs cached by a CDN server?}

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  Squid, in particular, uses the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}

There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$. This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.  But maybe the horse is sufficiently beaten by now...}

%\tsnote{What about content-based routing, or whatever that field is calling itself now?  A Bloom filter seems likely to be used there, and you'd want privacy for at least the content-seeker.}

@@

\if{0}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications (e.g. large CDN, P2P networks)
\item The main (im)possibility results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?  The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition! }
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret. (No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g. the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.  Hardly secret. \tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.  Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers); you create a Bloom filter for each record, one for each unique identifier in some cases.  Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.  In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g. ``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
\item The ``unsteady representation'' does not seem well founded.  Not sure what Bloom filter-like data structures would have randomized querying procedures.  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?)
\end{itemize}

\paragraph{Discussion. }
The traditional definition of Bloom filter soundness is information theoretic.  Effectively, it states that an IT adversary cannot find a false positive with probability more than some small value.  (That value is a function of the size of the set being represented, the representation size, the size of the universe, and the number of hash functions.)  This paper ([NY]) replaces the traditional IT notion with a computational notion, and casts it as a security experiment/goal.  Namely: given the set~$S$ that is represented by the Bloom filter, and access to an oracle for Bloom filter set-membership queries, an attacker must find a false positive.

\jknote{Of course, [NY] discusses an info-theoretic notion also. So in some sense what is really new here is consideration of adaptivity...}
\tsnote{Yes, defining soundness with respect to explicit adversaries, who are also adaptive, does seem to be the novel piece.}

Security relative to this notion appears to have some practical relevance.  [NY] points to whitelisting spam filters as an example.  That is, a Bloom filter is populated with set~$S$ of whitelisted email addresses, so a false positive translates to an attacker finding an email address that sneaks through the filter.  [NY] suggest a second example of content-caching servers that keep a Bloom filter of their own storage contents.  A false positive causes the server to search its local store, which is slow, only to find nothing. \tsnote{Question: in their security notions, the adversary wins by returning an $x^*$ that is not in~$S$ and is not one of the queries it asked to $B_2$; why the latter?  I understand why you shouldn't get credit for output something in~$S$ when~$S$ is given to you, but what if one of the queries to~$B_2$ is not in~$S$ and is a FP?  Shouldn't the adversary already win?}

To the first example, I suspect that spam filters are far more sophisticated than simply looking for whitelisted email addresses.  So the example feels artificial and overblown as practical motivation.  But more to the point, the security notion proposed by [NY] gives~$S$ ---the set of whitelisted email addresses--- to the adversary.  In practice, knowledge of these email addresses may be more damaging than creating a false-positive email address! (Keep in mind that the attacker wins, in this scenario, by creating any email address that passes the filter, even ones that bear no resemblance to real email addresses.)  From this perspective, the [NY] security definition is narrow in its scope, even assuming it says something useful about spam filtering.

\jknote{Yes, although another way to interpret this is that the adversary cannot find a false positive EVEN IF it had the whitelisted email addresses, even if in practice it does not.}
\tsnote{Fair enough. And this potentially unrealistic attack is preventable by a simple countermeasure.  That said, I'm not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.  (See below.)  } \tsnote{Also, while the adversary is given~$S$ (the whitelisted email addresses), the hash functions used to create the Bloom filter are \emph{secret}.  I'm not convinced this is realistic.}

I am less critical of the second example, although this is mostly because I feel ignorant of how real CDNs operate.  However, I believe that the following is common.  Say I'm a caching server.  If my Bloom filter tells me that some requested content is not locally stored, then I check the Bloom filters of my network neighbors, these having been shared with me.  When a neighbor's Bloom filter is positive for the requested content, I contact that neighbor, and that neighbor only.  (If no neighbor has it, then I have to retrieve it from some slower and more distant source, like the Web.)  Now, the [NY] construction uses a PRP, meaning that a secret key is involved in evaluating the Bloom filter.  Thus, I need to know the secret keys of my neighbors in order to operate in the way just described.  This seems troublesome in practice, at CDN-sized scale. (Also in P2P networks, where peers are joining/leaving frequently.)  Thus, their solution to a (potentially) real problem seems to be a non-solution.

Note that there is at least one way to avoid this knowledge of secret keys issues.  Namely, assume that content-caching servers distinguish between Bloom filter queries that originate from outside the CDN (e.g. users’ browsers) and those from within (e.g. other servers), and that the attacker only makes the former type of queries.  Then each server could store its neighbors’ Bloom filters in the clear, as normal, and only use the PRP construction when responding to external queries.  I don’t know how realistic this separation of queries is, in practice, nor how easy it would be to deploy such a strategy.  I also don’t know if this restricted attack scenario is interesting or plausible.

Moving on, the paper spends too much time asking and answering questions that are interesting to theoreticians, only.  Specifically, the relationship between the existence of one-way functions and Bloom filters that are secure relative to their definition.

\jknote{Agreed. =)}

Finally, the Bloom filter formalization that is given does not obviously capture traditional Bloom filters!  Traditionally, both Bloom filter population and querying procedures use hash functions $h_1,h_2,...h_k$ that each map from some universe $U$ to $[m]$, where $m$ is the bit-length of the array $M$ that represents a given set $S$.  These hash functions are missing from the authors’ definition, apparently swept into the algorithms $B_1$ (population) and $B_2$ (querying).  I don't really understand how, though. They allow $B_1$ to be randomized, which would let $B_1$ pick the hash functions.  But the security definition provides no way for $B_1$ to share these with $B_2$.  So how would $B_2$ be able to process set-membership queries?  (Note: based on how they define the size of the representation $M$, $B_1$ cannot include descriptions of $h_1, h_2, \ldots , h_k$ in $M$.  They really mean $M$ to be the array that represents the set $S$.)  In general, their formalization of the Bloom filter primitive is badly underdefined.

\jknote{You had me for a minute...but actually I think the representations of the hash functions ARE included in the representation. This is not explicit, but is consistent with the way they state their positive result in the computational setting (“...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”); more importantly, it seems explicit from their treatment of the IT case.}

\tsnote{Perhaps.  I'm still not convinced.  If you read the text preceding the statement of Theorem 1.2 (page 4), you'll see their discussion of lower bounds on “memory” required for a given set size and FP rate.  This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.  It says nothing about the description of the hash functions needed to populate the array.  In fact, this lower bound is for any method of representing set $S$ in a bit array, not only for hashing-based methods.
%
Maybe they are defining “memory” differently in this discussion than in their theorems.  This would be annoying, and I think it isn't the case.  So for the moment, I'll continue to hold my position on this.
%
(I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.  But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
%
But for the sake of argument, say that their representation size~$m$ does include the description of the hash functions.  To me, this is a clunky way to handle this matter.  For one thing, it doesn't play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.  (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?
%
I'll agree that this syntactic issue does not matter for theorem statements such as ``...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…''.  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array. Concretely: in the abstract they say ``... we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''. (Note that this~$g$ is only used to determined \emph{what} is stored at the indicated array/table positions, not \emph{where}.)  Thus they are not considering the size of the hash functions~$h_1,h_2$ that are used to indicated which cells of~$D$ need to be altered.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}

Finally, the security definitions do not give the adversary access to the hash functions that created the representation; effectively, they are secret. \tsnote{Unless they are assuming that the hash functions are fixed, part of the algorithms $B_1$ and $B_2$?  In which case, $A$~knows them too; and the security notion gives~$S$ to~$A$, so...}  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k). However, Squid employs a very efficient method using a fixed number - four. {\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks. Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e. an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above. This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}

\paragraph{Obvious Tasks. }

\begin{enumerate}
\item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature. (See wikipedia, a section of which I've pasted in at the end of this doc.) \tsnote{5/23: lots of uses to consider --CDNs/load balancers, peer-to-peer networks, medical record linkage, model checking, etc.  Might be good to try to characterize by, say, setting (distributed vs. local), typical BF instance size (e.g. local whitelist of emails = ``small'', CDN server-cache summary = ``large''), security concerns, and estimated severity of security violation (e.g. FP at CDN server = ``low'' or ``medium'', deanonymizing medical record = ``high'').  Just throwing out ideas...}
\item Work out a proper “cryptographic” syntax for the Bloom filter primitive.  (Possibly something more general, see number 5.)
\item Establish security notions that are appropriate for broader use cases (e.g. privacy of~$S$, privacy of the representation~$M$, authenticity of representation~$M$), single Bloom filter vs.\ multiple Bloom filter settings (e.g. attacking a CDN by querying multiple servers)
\item Develop constructions that are secure and are supported by a practice-informed argument for deployment
\item Break some stuff :-)
\item Starting with a secure ``basic'' Bloom filter, develop results for more complicated Bloom filter constructions (e.g. hierarchical Bloom filters, attenuated BFs), and Bloom-filter-based protocols
\item Expand from Bloom filters to  approximate-set-membership primitives, i.e. more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense~---i.e. it doesn't explode the scope, it doesn't send us off too far into theoryland.
\item Expand more generally to hash-based approximate set operations, e.g.\ minhash methods for approximating $J(A,B)$ for sets $A,B$.  Note: this should be done only if it makes sense~---i.e. it doesn't explode the scope, it doesn't send us off too far into theoryland.
\end{enumerate}

\jknote{I think privacy is an interesting question. I also thought that both privacy and soundness could be considered both in the setting when the representation is “hidden” from the adversary (as in the paper under discussion) as well as in the setting where the representation is public. [Ahh...I see you have some similar thoughts further below.] Some thoughts about this:
(1) Privacy in the “hidden” setting. Here the idea would be that queries about whether $x \in S$ reveal only the result of the query and nothing else;
(2) Privacy in the “public” setting. Here we could assume the elements of~$S$ have high entropy, and~$S$ has low density, and require that the attacker cannot find~$x \in S$ even when given the representation(!) I see no reason why this should not be achievable in the random oracle model, or possibly even in the standard model;
(3) Soundness in the “public” setting. Note that if the soundness is 0.5 then the attacker can simply guess random elements until it finds a false positive. So one way to approach this is to look at negligible soundness error only. Or, in the random oracle model, you could count queries to the RO and bound the attacker's success as a function of the number of queries it makes.
}

\paragraph{From the Wikipedia page...}
Google BigTable, Apache HBase and Apache Cassandra use Bloom filters to reduce the disk lookups for non-existent rows or columns. Avoiding costly disk lookups considerably increases the performance of a database query operation.[7][8]
The Google Chrome web browser used to use a Bloom filter to identify malicious URLs. Any URL was first checked against a local Bloom filter, and only if the Bloom filter returned a positive result was a full check of the URL performed (and the user warned, if that too returned a positive result).[9][10]
The Squid Web Proxy Cache uses Bloom filters for cache digests.[11]
Bitcoin uses Bloom filters to speed up wallet synchronization.[12][13]
The Venti archival storage system uses Bloom filters to detect previously stored data.[14]
The SPIN model checker uses Bloom filters to track the reachable state space for large verification problems.[15]
The Cascading analytics framework uses Bloom filters to speed up asymmetric joins, where one of the joined data sets is significantly larger than the other (often called Bloom join[16] in the database literature).[17]
The Exim mail transfer agent (MTA) uses bloom filters in its rate-limit feature.[18]

\fi

>>>>

\section{Introduction}
\label{sec:intro}
\tsnote{Skeleton text from old intro.  (Full version of old intro now
  in an appendix.}
We revisit the formalization of Bloom filters~\cite{xxx} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admiting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.

Bloom filters have a broad range of practical applications, for
example, in content-distribution networks, large database query
processing, routing algorithms for peer-to-peer networks, protocols
for establishing linkages between medical-record databases, fair
routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need
  citations}

@@
